Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2017-01-06 Papers/2017/LogicaUniversalis-HajekAndersonControversy/main.tex
Clarify reference to metis

In our
experiments we have utilized the proof assistant Isabelle/HOL
\citep{Isabelle} together with the automated higher-order reasoners
Leo-II \citep{Leo-II}, Satallax \citep{Satallax}, Metis
\citep{Hurd03first-orderproof}, and Nitpick \citep{Nitpick}.

>>>>

In our
experiments we have utilized the proof assistant Isabelle/HOL
\citep{Isabelle} together with the external automated higher-order provers
Leo-II \citep{Leo-II} and Satallax \citep{Satallax}, called through Sledgehammer. Sledgehammer analyzes the proofs generated by these provers and tells which axioms or previously proven lemmas are need to reconstruct the proof inside Isabelle using Isabelle's \emph{metis} method \citep{PaulsonSusanto}, which relies on a Isabelle porting of the resolution-based first-order prover Metis
\citep{Hurd03first-orderproof}. To find counter-examples, we used Nitpick \citep{Nitpick}, also through Isabelle.
